% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Benjamin M. Dawson}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  \href{http://are.ucdavis.edu/en/}{University of California Davis} \\
  Agriculture and Resource Economics \\
 One Shields Ave. \\
 Davis, CA 95616\\
 
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:@ucdavis.edu}{\tt bdawson@ucdavis.edu} \\
    Homepage: & \href{http://benjaminmdawson.com}{\tt http://benjaminmdawson.com} \\
  \end{tabular}
\end{minipage}

\section*{Research Interests}
\begin{itemize}
\item Environmental \& Energy Economics, Econometrics, Industrial Organization, Energy \& Climate Policy.
\end{itemize} 

\section*{Education}

\begin{itemize}
  \item Ph.D. Candidate, Agriculture and Resource Economics, UC Davis, 2016 -- present
  \item M.E.Sc. Environmental Economics, Yale University, 2016.
  
  \leftskip 0.5in
 \parindent -0.5in
  \subitem Thesis: \emph{GDP, Weather, and Growth: Consequences for Climate-Economy Modeling}
  
  \leftskip 0.0in
  \item B.S. Ecological Engineering, Oregon State University, 2011.
  
  \leftskip 0.5in
 \parindent -0.5in
  \subitem Thesis: \emph{A Technological and Economic Feasibility Study of Algal Biofuel Production}
\end{itemize}

\section*{Research Experience}
\begin{itemize}
\item {\bf Current Projects}

\leftskip 0.5in
\parindent -0.5in
\subitem Graduate Student Researcher at the Davis Energy Economic Program (DEEP); working with James Bushnell and David Rapson (2017 -- present) \\
%\subitem Economic impacts of climate change (2015 -- present) \\


\leftskip 0in
\item {\bf Past Projects}

\leftskip 0.5in
\parindent -0.5in
\subitem Research Assistant for Oswald Schmitz and Robert Mendelsohn (2015 -- 2016)
\subitem Research Assistant for Ken Gillingham (2014 -- 2015)
\subitem Eco-informatics Summer Institute (NSF Research Grant) (2009)
\end{itemize}

\section*{Previous Employment}
\begin{itemize}
\leftskip 0in
\item {\bf Past Employment}

\leftskip 0.5in
\parindent -0.5in
\subitem Research and policy analyst with E9 Energy Insight, Inc. (2014 -- 2016) 
\subitem Energy system intern at the Rocky Mountain Institute (2015)
\subitem Co-founder and board member at Rogue Climate (2013 -- 2015)
\subitem Riparian ecologist at R2 Resource Consultants, Inc. (2013 -- 2014)
\subitem Home energy building modeler at Southern Oregon Green Rating Services (2014)
\end{itemize}

\section*{Publications}
\begin{itemize}
\leftskip 0in
\item {\bf Journal Articles}

\leftskip 0.5in
\parindent -0.5in
\subitem Mendelsohn, Robert, Iain C. Prentice, Oswald Schmitz, Benjamin Stocker, Robert Buchkowski and \textbf{Benjamin Dawson}. 2016. The Ecosystem Impacts of Severe Warming. \textit{American Economic Review, Papers and Proceedings}, 106(5): 612-14. \\

\leftskip 0in
%\item {\bf Working Papers}
%
%\leftskip 0.5in
%\parindent -0.5in
%\subitem \textbf{Dawson, B}. Weather, Climate and Production: Estimating Climate Change Impacts in the United States 

\end{itemize}

\section*{Presentations}
%\begin{itemize}
%\item {\bf 2018}
%% Need this space
%
%\leftskip 0.5in
%\parindent -0.5in
%\subitem Masters Student Research Colloquium 2016; Yale School of Forestry and Environmental Studies
%\end{itemize}

\begin{itemize}
\item {\bf 2016}
% Need this space

\leftskip 0.5in
\parindent -0.5in
\subitem Masters Student Research Colloquium 2016; Yale School of Forestry and Environmental Studies
\subitem Yale Energy and Environment Day 2016
\end{itemize}

\section*{Honors and Awards}

\begin{itemize}
  \item Provost's Fellowships in the Arts, Humanities and Social Sciences, 2016-2017
  \item National Science Foundation Graduate Research Fellowship, Honorable Mention, 2014, 2015
\end{itemize}

\section*{Skills}
\begin{itemize}
\item {\bf Programming}
\subitem R, Stata, GIS, MATLAB, Python
\item {\bf Methods}

\leftskip 0.5in
\parindent -0.5in

\subitem Davis Classes: Microeconomic Theory, Advanced Econometrics, and Applied Microeconomics, Industrial Organization, Environmental Economics, Public Economics
\subitem{Yale Classes: Energy Economics and Policy Analysis, Climate Change and Energy Economics, Enivironemntal Economics (Ph.D. Field Course), Environmental Economics, Advanced Quantitative Methods, Econometrics, Microeconomics, Energy Technology Innovation}

\end{itemize}

% \bigskip
\medskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}
